COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-12-18 main.tex
Add motivation for dust circularizing

>>>>

To construct a radial dust profile, we begin by making the assumption that any dust generated by collisions is strongly coupled to the 
gas. For a dust grain larger than the mean free path of the gas particles, the timescale to damp its eccentricity is given by 
\citep{1976PThPh..56.1756A}

\begin{equation}\label{eq:t_edamp}
    t_{e, damp} = \frac{8 s \rho}{3 e C_{D} \rho_{g} v_{th}}.
\end{equation}

where $m$, $e$ and $s$ are the mass, eccentricity and radius of the dust grain. $C_{D}$ is a drag coefficient which is of order unity, $
\rho_{g}$ is the local density of the gas and $v_{th}$ is its thermal speed. At 3 AU, the gaseous component of the solar nebula has a 
density of $4 \times 10^{-10}$ g cm$^{-3}$ and a typical thermal speed of $10^{5}$ cm s$^{-1}$ \citep{1981PThPS..70...35H}. For a 1 
mm dust grain with a density of 1 g cm$^{-3}$ and an eccentricity of 0.05, the damping timescale is $4 \times 10^{-3}$ years. This is 
orders of magnitude smaller than the collision timescale, therefore we expect that collisionally generated dust grains will immediately 
couple to the gas.

Operating under this assumption, a map of the relative concentration of second-generation dust can be constructed from simply the cylindrical distance at which the collisions occur. This is shown in the top panels of figure \ref{fig:coll_hist_r}, where the left side corresponds to the CJ simulation and the right side corresponds to EJ.
